A Mechanical Formalization of Higher-Ranked Polymorphic Type Inference

### 2019-05-29 sections/Overview.tex
ML Essence

In the above unification problem, all variables are implicitly bound in the same
global scope. 
\bruno{Some constraint solving algorithms for Hindley-Milner type
  inference use similar ideas, but are more careful tracking the
  scopes of variables~\cite{}. However they have separate phases for 
constraint generation and solving.}
Recent unification algorithms for dependently-typed languages
are also more explicit about scopes. For instance, \citet{Reed2009} represents a unification
problem as $\Delta \vdash P$ where $P$ is a set of equations to be solved and $\Delta$ is
a (modal) context. \citet{Abel2011higher} even use multiple contexts within a unification problem.
Such a problem is denoted $\Delta \Vdash \mathcal{K}$ where the meta-context
$\Delta$ contains all the typings of meta-variables in the constraint set
$\mathcal{K}$. The latter consists of constraints like $\Psi \vdash M = N : C$
that are equipped with their individual context $\Psi$. While accurately tracking
the scoping of regular and meta-variables, this approach is not ideal because it
repeatedly copies contexts when decomposing a unification problem, and
later it has to 
substitute solutions into these copies.

>>>>

In the above unification problem, all variables are implicitly bound in the same
global scope. 
Some constraint solving algorithms for Hindley-Milner type
  inference use similar ideas, but are more careful tracking the
  scopes of variables~\cite{remy-attapl}. However they have separate phases for 
constraint generation and solving.
Recent unification algorithms for dependently-typed languages
are also more explicit about scopes. For instance, \citet{Reed2009} represents a unification
problem as $\Delta \vdash P$ where $P$ is a set of equations to be solved and $\Delta$ is
a (modal) context. \citet{Abel2011higher} even use multiple contexts within a unification problem.
Such a problem is denoted $\Delta \Vdash \mathcal{K}$ where the meta-context
$\Delta$ contains all the typings of meta-variables in the constraint set
$\mathcal{K}$. The latter consists of constraints like $\Psi \vdash M = N : C$
that are equipped with their individual context $\Psi$. While accurately tracking
the scoping of regular and meta-variables, this approach is not ideal because it
repeatedly copies contexts when decomposing a unification problem, and
later it has to 
substitute solutions into these copies.

### 2019-05-29 sections/introduction.tex
ML Essence

\item {\bf A fully mechanized formalization of type inference with
  higher-ranked types:} Our work presents the first fully mechanized formalization
  for type inference of higher ranked types. The formalization is done in the
  Abella theorem prover~\cite{AbellaDesc} and it is available
  online at \url{http://TODO}.\bruno{fill url please!}

>>>>

\item {\bf A fully mechanized formalization of type inference with
  higher-ranked types:} Our work presents the first fully mechanized formalization
  for type inference of higher ranked types. The formalization is done in the
  Abella theorem prover~\cite{AbellaDesc} and it is available
  online at \url{https://github.com/JimmyZJX/TypingFormalization}.
